On Logic Embeddings and G\"odel's God

### 2015-04-05 Papers/2014/WADT/WADT-4pages.tex
Add bibitem for CSR paper

\bibitem{J22}
G.~Sutcliffe and C.~Benzm{\"u}ller.
\newblock Automated reasoning in higher-order logic
  using the {TPTP THF} infrastructure., {\em J. of Formalized Reasoning},
  3(1),  1--27, (2010).

>>>>

\bibitem{J22}
G.~Sutcliffe and C.~Benzm{\"u}ller.
\newblock Automated reasoning in higher-order logic
  using the {TPTP THF} infrastructure, {\em J. of Formalized Reasoning},
  3(1),  1--27, (2010).

\bibitem{CSR}
C.~Benzm{\"u}ller and B. Woltzenlogel Paleo.
\newblock Interacting with Modal Logics in the Coq Proof Assistant, {\em 10th International Computer Science Symposium in Russia (CSR)}, 2015.
